---
title: "Quiz 5"
output: html_document
---

# Question 1

What happens when you run the following R code?

```{r}
counter <- 1

while(counter < 3){
  print(counter)
}
```

- It prints 1, 2, and 3, then stops
- It prints 1 and 2, then stops
x It prints 1 repeatedly and never stops
- It prints 1, 2, and 3, then stops

# Question 2

Consider the function:

```{r}
safe_div <- function(x, y) {
  if (y == 0) {
    return("Division not possible")
    print("Trying to divide by zero...")
  }
  return(x / y)
}
```
```{r}
safe_div(10, 0)
```

What happens when you run `safe_div(10, 0)`?

- It prints "Trying to divide by zero..." and returns NA
- The function returns `x / y`
- It returns "Division not possible" and prints "Trying to divide by zero..."
x It returns "Division not possible" and the print statement is ignored

# Question 3

Which of the following is a correct anonymous-function rewrite of:

```{r}
add <- function(x) {
  return(x + 3)
}

add(2)
```

```{r}
(function(x) x + 3) 2
```
- `(x) function x + 3 (2)`
- `function x x + 3 (2)`
x `(function(x) x + 3)(2)`
- `(function(x) x + 3) 2`

# Question 4

In the function documentation shown below, what does the `Args:` section describe?

```{r}
my_summary <- function(v) {
  # Calculates a simple summary statistic for a numeric vector.
  #
  # Args:
  #   v (num): a numeric vector whose elements will be processed.
  #
  # Returns:
  #   value (num): a single numeric value representing the sum.
}
```

- The order in which operations inside the function are executed
- The objects that will be returned by the function
- The package dependencies of the function
- The objects created inside the function
x The input (or inputs) the function expects, along with its/their data type

# Question 5

You defined the following function using `dplyr` and the curly-curly operator:

```{r}
custom_summary <- function(data, col) {
  data %>%
    summarize(
      mean_value = mean({{ col }}),
      sd_value   = sd({{ col }})
    )
}

custom_summary(df, age)
```
Practice
```{r}
# Notice that col is just the argument name
custom_summary <- function(data, col) {
  data %>% 
    summarize(
      mean_value = mean({{col}}),
    )
}
#library(utils)
#write.csv(mpg, "mpg.csv")
```

Use the `custom_summary` with one column
```{r}
custom_summary(mpg, cty)
```

What is the purpose of the `{{ col }}` syntax here?

- Because without `{{ }}`, when you call the function `dplyr` will ignore the literal column name `col` and automatically guess the correct column (e.g., `age`) based on the data.
x Because without `{{ }}`, when you call the function `dplyr` will look for a column literally named `col` instead of using the column passed to the function (e.g., `age`).
- Because `{{ }}` makes the function run faster and it is a general good coding style practice when using custom functions with `dplyr`.
- Because without `{{ }}`, when you call the function `dplyr` defaults to the first column in the data unless instructed otherwise.

# Question 6

You run the following code:

```{r}
mutate(df, category = case_when(
  score > 50 ~ "Pass",
  score > 80 ~ "High Pass",
  TRUE ~ "Fail"
))
```


A student with `score = 90` will be labeled...

- "Pass", because `case_when()` assigns the first matching condition and stops evaluating the rest
- An error, because the conditions overlap
- "High Pass", because `case_when()` evaluates all conditions and picks the most specific match
- "Fail", because 90 does not satisfy any condition

# Question 7

Table A has 5 rows, with a key value `"x"` appearing 2 times. Table B has 3 rows, with the same key `"x"` appearing 2 times. If you `inner_join()` A and B by that key, how many rows involving key `"x"` appear in the result?

- 0
- 5
- 4
- 2

# Question 8

Where should global code chunk options be set in an R Markdown document?

- Inside each chunk that needs to follow the global settings
- At the end of the document after all chunks have run
- In a setup code chunk near the beginning of the file
- In the YAML header at the top of the document
